Flexibility of interactions depends on habitat suitability

### 2019-09-01 paper/manuscript.Rmd
A first attempt for the intro P4

There are two main processes involved in whether two species in a community interact or not.
The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.
Under this rationale, when, for example,  a deep-rooted co-evolutionary history leads to optimally matched traits, the interacting species can obtain a substantial benefit from this interaction. 
Contrastingly, we would expect a lower per-capita benefit from interactions with low trait matching.
The second is a neutral process underpinned by the abundance of the interacting species. 
All else being equal, when the abundance of a species is high, their potential encounter rate is also high, and therefore there is a higher probability to interact than if it were rare.

@@

@@

 small number of partner species are thought to benefit largely from each  deeper co-evolutionary history that, through trait matching
Species with a small number of partners, specialists, are often deemed to 
Species with a large number of interactions, generalists, benefits relatively

>>>>

There are two main processes involved in whether two species in a community interact or not.
The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.
Under this rationale, when, for example, a deep-rooted co-evolutionary history leads to optimally matched traits, the interacting species can obtain a substantial benefit from this interaction. 
Contrastingly, we would expect a lower per-capita benefit from interactions with low trait matching.
The second is a neutral process underpinned by the encounter rate of the interacting species. 
All else being equal, when the encounter rate of interacting species is high there is a higher probability to interact than if the rate were smaller, for example due to species rarity.

@@

When looked from an Eltonian-niche lens, one way the environment can influence wether two species interact or not is based on, what we call, stress-induced hypotheses of interaction turnover. 
These hypotheses are rooted in the co-evolutionary processes that determine the quality of an interaction partner. 
Environmental induced stress can

Another way

In a pollination context, it can for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007)
.

Second, and oare more subtle, mechanism through which enviroment can determine interactions is
This is so because , species distributions are strongly determined 
At the basis of species distrFormally, the fundamental "Grinellian" niche of a species is determined by the set of environments where a species has a positive groth rate when rare. 
The environement, 
From a "Grinellian" niche perspect
Framed from a niche perspective,

@@

HYPOTHESIS: many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al. 1991). Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al. 2010, Guimaraes et al. 2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al. 2016).
